---
title: "HW05"
author: "Julius Mwangi"
date: "June 10, 2018"
output: html_document
---

#1.	Data Munging (30 points): Utilize yob2016.txt for this question. 
##a. 
```{r}
yob2016 <- read.csv("C:/Users/28911016/Desktop/Hesabu/2DScience/yob2016.txt", sep=";")
View(yob2016)
head(yob2016)
colnames(yob2016) <- c("names","gender","frequency")
summary(yob2016)

```
##b.Display the summary and structure of df
```{r}
summary(yob2016)
```
##c.

*I had already cleaned the data before running this code below, by idnetifying the mispelt names as "Fionayyy;F;1547"
```{r}
grep("yyy",yob2016)
```

##d.
```{r}
save(yob2016, file = "y2016")
```
#2.Data Merging
```{r}
yob2015 <- read.csv("C:/Users/28911016/Desktop/Hesabu/2DScience/yob2015.txt", sep=",")
names(yob2015) <- c("names", "gender", "frequency")
View(yob2015)
summary(yob2015)
y2015<-(yob2015)
```
##2.b	Display the last ten rows in the dataframe.  

```{r}
tail(y2015, 10)
```
The last ten names all start with "Z", each name was used 5 times , and their gender is Male

```{r}
names(yob2016)[names(yob2016) == "names_2015"] <- "names_2016"
final<-merge(yob2016,y2015,by="names")
summary(final)

```
#3.	Data Summary (30 points): Utilize your data frame object final for this part.
##a.Create a new column called "Total" in final that adds the amount of children in 2015 and 2016 together.  In those two years combined, how many people were given popular names?

```{r}
final$Total <- final$frequency.x + final$frequency.y
summary(final$Total)
head(final)

```
35 people were given popular names

##b.	Sort the data by Total.  What are the top 10 most popular names?
```{r}
bytotal <- final[order(final$Total),] 
head(bytotal,10)
```
##c.	The client is expecting a girl!  Omit boys and give the top 10 most popular girl's names.

```{r}
bytotal <- final[order(final$Total),]
bytotal = subset(bytotal, gender.x == "F", gender.y =="F")
summary(bytotal)
head(bytotal,10)
final2<-head(bytotal,10)
write.csv(final2, file = "final2.csv")
```

Results remains as above - must be doing something wrong.
